---
title: "Reproducibility Report: Group B Choice 1"
output:
  html_document:
    toc: true
    toc_float: true
---

-------

For this exercise, please try to reproduce the results from Experiment 1 of the associated paper (Farooqui & Manly, 2015). The PDF of the paper is included in the same folder as this Rmd file. 

#### Methods summary: 

Participants (N=21) completed a series of trials that required them to switch or stay from one task to the other. One task was to choose the larger value of the two values if surrounded by a green box. The other task was to choose the value with the larger font if surrounded by a blue box. Subliminal cues followed by a mask were presented before each trial. Cues included "O" (non-predictive cue), "M" (switch predictive cue), and "T" (repeat predictive cue). Reaction times and performance accuracy were measured.

------

#### Target outcomes: 

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Experiment 1):

> Performance on switch trials, relative to repeat trials, incurred a switch cost that was evident in longer RTs (836 vs. 689 ms) and lower accuracy rates (79% vs. 92%). If participants were able to learn the predictive value of the cue that preceded only switch trials and could instantiate relevant anticipatory control in response to it, the performance on switch trials preceded by this cue would be better than on switch trials preceded by the nonpredictive cue. This was indeed the case (mean RT-predictive cue: 819 ms; nonpredictive cue: 871 ms; mean difference = 52 ms, 95% confidence interval, or CI = [19.5, 84.4]), two-tailed paired t(20) = 3.34, p < .01. However, error rates did not differ across these two groups of switch trials (predictive cue: 78.9%; nonpredictive cue: 78.8%), p = .8.

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files

# #optional packages:
# library(broom)
```

## Step 2: Load data

```{r warning=FALSE}
# This reads all the participants data (each is in a seperate xls file) in and combines them into one dataframe
# Each xls has 250 rows, the rest is their calculations using excel, which we don't want in the data
files <- dir('data/Experiment 1')

data <- data.frame()
id <- 1
for (file in files){
  if(file != 'Codebook.xls'){
    temp_data <- read_xls(file.path('data/Experiment 1', file))
    temp_data$id <- id
    id <- id + 1
    temp_data <- temp_data[1:250, ]
    data <- rbind(data, temp_data)
  }
}
```

## Step 3: Tidy data

Each row is an observation. The data is already in tidy format.

## Step 4: Run analysis

### Pre-processing

```{r}
# O or 2 is non-predictive, M or 8 is switch predictive, T or 4 is repeat predictive; need to rename some of the values to make them consistent
data$Prime[data$Prime == "2"] <- "O"
data$Prime[data$Prime == "8"] <- "M"
data$Prime[data$Prime == "4"] <- "T"
```

### Descriptive statistics

> Performance on switch trials, relative to repeat trials, incurred a switch cost that was evident in longer RTs (836 vs. 689 ms) 

```{r}
# reproduce the above results here
# 1 is repeat trial, 2 is switch trial
data %>%
  group_by(TrialType) %>%
  summarise(median(RT))
```

> Performance on switch trials, relative to repeat trials, incurred a switch cost that was evident in [...] lower accuracy rates (79% vs. 92%)

```{r mean_Correct_Response}
# reproduce the above results here
data %>%
  group_by(TrialType) %>%
  summarise(mean(RespCorr))
```

Now you will analyze Predictive Switch Cues vs Non-predictive Switch Cues. Let's start with reaction time.

> This was indeed the case (mean RT-predictive cue: 819 ms; nonpredictive cue: 871 ms; ... )

```{r mean Prime RT}
# reproduce the above results here
data %>%
  group_by(Prime) %>%
  summarise(mean(RT))
```

Next you will try to reproduce error rates for Switch Predictive Cues vs Switch Non-predictive Cues.

> However, error rates did not differ across these two groups of switch trials (predictive cue: 78.9%; nonpredictive cue: 78.8%)

```{r Prime Accuracy}
# reproduce the above results here
data %>%
  group_by(Prime) %>%
  summarise(mean(RespCorr))
```

### Inferential statistics

The first claim is that in switch trials, predictive cues lead to statistically significant faster reaction times than nonpredictive cues.

> ... the performance on switch trials preceded by this cue would be better than on switch trials preceded by the nonpredictive cue. This was indeed the case (mean RT-predictive cue: 819 ms; nonpredictive cue: 871 ms; mean difference = 52 ms, 95% confidence interval, or CI = [19.5, 84.4]), two-tailed paired t(20) = 3.34, p < .01.

```{r Prime RT test}
# reproduce the above results here
# filter out Prime = T bc we only need O (non-predictive) and M (switch predictive) for this analysis
filtered_data = data %>%
  filter(Prime != "T")

# change data from long to wide 
filtered_data_wide = filtered_data %>%
  pivot_wider(names_from = Prime, 
              values_from = RT)

# I ran into an issue with changing my data to wide form so I couldn't do a paired t-test due to issues with the number of subjects in each condition. This is how I would have done the paired t-test: t.test(RT ~ Prime, paired=TRUE, data=filtered_data_wide)

# However I do still want to have some type of result to show so here's the non-paired t test:
t.test(RT ~ Prime, data=filtered_data)
```

Next, test the second claim.

> However, error rates did not differ across these two groups of switch trials (predictive cue: 78.9%; nonpredictive cue: 78.8%), p = .8.

```{r mean Prime accuracy test}
# reproduce the above results here

# Again, because I couldn't successfully change my data from long to wide, I couldn't do a paired t-test due. This is how I would have done the paired t-test: t.test(RespCorr ~ Prime, paired=TRUE, data=filtered_data_wide)

# Again, here is the non-paired t-test because I want to at least have some result to show: 
t.test(RespCorr ~ Prime, data=filtered_data)

```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> I was mostly able to reproduce all of the descriptive statistics. However, there were some minor differences between my results and the original results. However, the reaction time means that I got for Predictive Switch Cues vs Non-predictive Switch Cues were very different in that my results showed that reaction time was shorter in the non-predictive switch condition than the predictive condition, which is the opposite of the original finding. Unfortunately, I wasn't able to reproduce the t-test results. Based on an error I ran into while trying to perform the t-test on the long data, I deduced that I had to convert the data from long to wide first. However, I had a lot of difficulty converting the data to wide, so I was not able to run a paired t-test. 

How difficult was it to reproduce your results? 

> This one was pretty difficult because there was more data wrangling that needed to be done before I could perform the main tests. I struggled a lot with getting the data in the form that it needed to be in.

What aspects made it difficult? What aspects made it easy?

> Something that made this difficult in particular was confusion about how things were labeled in the data. I did see later on that there was a codebook in the folder that ended up being helpful, but there were still some things that weren't explained (i.e., what 2, 4 and 8 meant in the Prime column). Something else that was confusing and made reproducability difficult was that there were only 2 trial types discussed in the paper, but there were 3 in the data (values 0, 1, or 2). The paper never mentioned a third trial or what the 0 represented, so this was confusing. The codebook did end up making understanding this assignment easier, but I didn't know there was a codebook until I had already spent a lot of time on this problem, so I think it could be made more clear/explicit in the future. 
