---
title: "Reproducibility Report: Group A Choice 3"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

-------

For this exercise, please try to reproduce the results from Experiment 6 of the associated paper (Shah, Shafir, & Mullainathan, 2015). The PDF of the paper is included in the same folder as this Rmd file. 

#### Methods summary:

The authors were interested in the effect of scarcity on people's consistency of valuation judgments. In this study, participants played a game of Family Feud and were given either 75 s (budget - "poor" condition) or 250 s (budget - "rich" condition) to complete the game. After playing the game, participants were either primed to think about a small account of time necessary to play one round of the game (account -"small" condition) or a large account (their overall time budget to play the entire game, account - "large" condition.) Participants rated how costly it would feel to lose 10s of time to play the game. The researchers were primarily interested in an interaction between the between-subjects factors of scarcity and account, hypothesizing that those in the budget - "poor" condition would be more consistent in their valuation of the 10s regardless of account in comparison with those in the budget - "rich" condition. The authors tested this hypothesis with a 2x2 between-subjects ANOVA.

------

#### Target outcomes: 

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Experiment 6):

> "One participant was excluded because of a computer
malfunction during the game. Time-rich participants
rated the loss as more expensive when they thought
about a small account (M = 8.31, 95% CI = [7.78, 8.84])
than when they thought about a large account (M = 6.50,
95% CI = [5.42, 7.58]), whereas time-poor participants’
evaluations did not differ between the small-account
condition (M = 8.33, 95% CI = [7.14, 9.52]) and the large account
condition (M = 8.83, 95% CI = [7.97, 9.69]). A 2
(scarcity condition) × 2 (account condition) analysis of
variance revealed a significant interaction, F(1, 69) = 5.16,
p < .05, ηp2 = .07." (Shah, Shafir & Mullainathan, 2015)
------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(lsr)

# #optional packages:
# library(afex) #anova functions
# library(langcog) #95 percent confidence intervals
```

# Step 2: Load data

```{r}
# Just Experiment 6
data <- read_excel("data/study 6-accessible-feud.xlsx")
```

# Step 3: Tidy data

The data are already tidy as provided by the authors.

# Step 4: Run analysis

## Pre-processing

> One participant was excluded because of a computer malfunction during the game (Shah, Shafir, & Mullainathan, 2015, p. 408)

Note: The original paper does not identify the participant that was excluded, but it was later revealed through communication with the authors that it was participant #16. The exclusion is performed below. 

```{r}
# Participant #16 should be dropped from analysis 
excluded <- "16"

d <- data %>%
  filter(!Subject %in% excluded) #participant exclusions
```

## Descriptive statistics

> Time-rich participants rated the loss as more expensive when they thought about a small account (M = 8.31, 95% CI = [7.78, 8.84]) than when they thought about a large account (M = 6.50, 95% CI = [5.42, 7.58]), whereas time-poor participants’ evaluations did not differ between the small-account condition (M = 8.33, 95% CI = [7.14, 9.52]) and the large- account condition (M = 8.83, 95% CI = [7.97, 9.69]). (Shah, Shafir, & Mullainathan, 2015, p. 408)

```{r}
# reproduce the above results here
d %>%
  group_by(Cond) %>%
  summarise(Mean = mean(expense),CI = confint(lm(expense ~ 1), level = 0.95)) -> summary_d
```

## Inferential statistics

> A 2 (scarcity condition) × 2 (account condition) analysis of variance revealed a significant interaction, F(1, 69) = 5.16, p < .05, ηp2 = .07.

```{r}
# reproduce the above results here
two.way <- aov(expense ~ Slack*Large, data = d)
summary(two.way)
etaSquared(two.way)
```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> I was able to reproduce the means for each condition, but my confidence intervals are a little bit off from the original. They were close, but maybe I need to try bootstrapping to get them to be more accurate. As for the ANOVA interaction, I was able to reproduce the same results. The eta squared value (.063) was a little different from the original (.07), but very close.  

How difficult was it to reproduce your results? 

> It wasn't too difficult, especially since the data was easy to work with. However, I was confused at first because of the column names in the data, as I wasn't sure what Slack and Large meant. I was able to infer and use some process of elimination, but I think the data could have been labeled a bit more intuitively to help with interpretation.  

What aspects made it difficult? What aspects made it easy?

> Again, one aspect that made it difficult was not fully understanding what the column names represented. An aspect that made reproducability easy was that the data wasn't particularly messy. I didn't have to do much data wrangling or cleaning before reproducing the results, which made the entire process fairly convenient In addition, the results were described very clearly and with detail in the original paper, which helped me understand how to run the ANOVA and what I was looking for. In general, the article itself served as a useful reference. 
